### 2013-11-25 PositionPaper/incremental.tex
small changes

We propose an SLA guided continuous data provision and integration approach that proposes three steps  starting from the processing of the request  to the delivery of the result sets.

@@

The first stage of our proposed data integration and provision process is  defined as a vertical mapping of high level and agreed SLAs. Hig level SLA is expressed as macroscopic constraints: execution time, pay / no pay, data reliability, data source. The system  finds relevant service compositions that respond to the query  such that when combined, they meet the constraints imposed by the user. One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.

@@

When a potential Internet client requires a list of books, a composed web service is generated, in order to fetch each book (from the nearest warehouse where the book is available) and to put in motion the payment and packing procedures.
Depending on the location of the client, different conditions may apply on the selling and payment procedures.
So, for each country or region, a limited number of options may be available for payment, packaging and delivery.
Additionally, non-functional requirements, defined by SLA may apply.

In this context, the user supplies the list of books, his location and payment information and a composite web service should be generated to satisfy the order.
The generated service composition should pick each book at the nearest warehouse, in order to minimize the costs of delivery and processing.
Additional requirements, such as delivery time, may apply.

In order to produce a personalised service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
The specification of each available service is also considered (this specification is given by each cloud provider).
~\hfill\openbox
\end{example}

@@

As far as our knowledge, the incremental production of a solution is outside of the scope of the current solutions for rewriting service compositions and represents a challenge to the area.
~\hfill\openbox
\end{example}

>>>>

We propose an SLA guided, continuous data provision and integration approach that proposes three steps  starting from the processing of the request  to the delivery of the result sets.

@@

The first stage of our proposed data integration and provision process is  defined as a vertical mapping of high level and agreed SLAs. Higher level SLA is expressed as macroscopic constraints: execution time, pay / no pay, data reliability, data source. The system  finds relevant service compositions that respond to the query  such that when combined, they meet the constraints imposed by the user. One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.

@@

When an on-line client requires a list of books, a composed web service is generated, in order to fetch each book (from the nearest warehouse where the book is available) and to put in motion the payment and packing procedures.
Depending on the location of the client, different conditions may apply on the selling and payment procedures.
So, for each country or region, a limited number of options may be available for payment, packaging and delivery.
Additionally, non-functional requirements, defined by SLA may apply.

In this context, the user supplies the list of books, his location and payment information and a composite web service should be generated to fulfill the order.
The generated service composition should pick each book at the nearest warehouse, in order to minimize the costs of delivery and processing.
Additional requirements, such as delivery time, may apply.

In order to produce a personalised service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
The specification of each available service is also considered (this specification should be given by the service provider).
~\hfill\openbox
\end{example}

@@

As far as our knowledge, the incremental production of a solution is outside of the scope of the current methods for rewriting service compositions and represents a challenge to the area.
~\hfill\openbox
\end{example}

### 2013-11-25 PositionPaper/relwork.tex
small changes

Recent research works on SLA are devoted to the SLA extension to security concerns. Hale
and al. in \cite{6274042} propose an extension of the WSAgreement initially developed by the GRAAP
working group. The extension allows security constraints to be expressed over the service description
terms (SDTs) and the service level objectives (SLOs) of the SLA. Consequently, this leads to a certain kind of security expression interoperability and lets the client to be able to compare security level of different CSP. Luna and al
work \cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. The designed template is then used both to express user security requirements and CSP security provisions.

>>>>

The advent of cloud computing imposed a new model for resource managing.
The new model is not concerned with the \textit{limits} of resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources. 
Service Level Agreements (SLA)~\cite{SLA} can be used in thee context of cloud computing in order to establish those conditions.
SLAs are bounding contracts between each service provider and their clients.
The deployment of SLAs lies on two features: (i) the negotiation of conditions, agreed by both parts and (ii) the monitoring of these conditions during the use of each service.

=====================
Recent research works on SLA are devoted to the SLA extension to security concerns. Hale
and al. in \cite{6274042} propose an extension of the WSAgreement initially developed by the GRAAP
working group. The extension allows security constraints to be expressed over the service description
terms (SDTs) and the service level objectives (SLOs) of the SLA. Consequently, this leads to a certain kind of security expression interoperability and lets the client to be able to compare security level of different CSP. Luna and al
work \cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. The designed template is then used both to express user security requirements and CSP security provisions.
